Interactions with Domain Experts

### 2021-02-18 StateOfPractice/Methodology/Interactions with Domain Experts.tex
Some edits to the interaction with domain experts document

The purpose of the document is to describe the interactions with the domain
experts, which will be through 3 steps as follows,
\begin{itemize}
\item Step 1 - Introductory Meeting in Section \ref{introductory_meeting}. In
this meeting, we will be focusing on introducing the background and objectives
of the project and vetting some details and plans.
\item Step 2 - Measuring in Section \ref{qualities_measurements}. Vetting the
Domain Analysis, usability experiments, modifiability experiments, and
developer interviews are included in this step.
\item Step 3 - Concluding Meeting in Section \ref{concluding_meeting}. Our
second and the last meeting, aiming to be
one hour in duration. Results of ranking will be discussed.
\end{itemize}

>>>>

The purpose of the document is to describe the interactions with the domain
experts.  For each domain that is measured, a domain expert is a member of the
assessment team.  Their role is to provide their expertise on the domain and its
existing software.   The domain expert will typically be a faculty member.
Ideally their graduate students will also assist with the measurement process.

The interactions with the domain experts and their graduate students are divided
into 3 stages:

\begin{itemize}
\item Stage 1 - Introductory Meeting in Section \ref{introductory_meeting}. In
this meeting, we will be focusing on introducing the background and objectives
of the project and vetting the initial software list.  We will also discuss the
resources that the domain expert can make available for Stage 2.
\item Stage 2 - This stage isn't isolated to a single meeting, but is rather a
  series of measurement and assessment tasks, as described in Section
  \ref{qualities_measurements}.  During this stage the domain expert and their
  students will help with vetting the Domain Analysis, usability
  experiments, and modifiability experiments.  We will also interview the domain
  expert in this step, using similar questions to those that we are asking the
  developers.  (By developers, we mean the programmers that have created the
  programs in the domain that are being measured.)
\item Stage 3 - The domain expert interaction concludes with a final meeting, as
  detailed in Section \ref{concluding_meeting}.  In this meeting we will discuss
  the results of Stage 2 and go over the final ranking.
\end{itemize}
